---
title: "Cleaning social media data"
output: html_notebook
---

## Reddit datasets
* Employment:
  * 1. Query: all
  * 2. Query: top 100 subreddits.
  * 3. Query: likely-to-be-relevant subreddits.
  * 4. No-query: all data from likely-to-be-relevant subreddits.
* Vaccination:
  * 1. Query: all
  
## Twitter datasets.
* Employment:
  * 1. Query: all
* Vaccination:
  * 1. Query: all


## Cleaning
1a:
* Remove useless columns
* Done in python scripts (Reddit/main and Twitter/main)

1b: 
* Remove any anomalies/useless posts missed by filters (e.g. blanks/removed/NaN, etc.)
* All lower-case.
* Tokenize
* Noise removal (punctuation, special characters, stopwords).

2:
* Stemming

```{r}
knitr::opts_chunk$set(echo = TRUE, include = TRUE, warning = FALSE)
```


```{r}
rm(list = ls())

# Run script to create the reddit subsets
# source("reddit_subsets.R", local = knitr::knit_global())
```

```{r}
# Load functions to clean sm data.
source("cleaning_funcs.R", local = knitr::knit_global())
```


```{r}
# # Load data
# reddit_emp_1 <- load_data('Reddit', 'Employment', 1)
# reddit_emp_2 <- load_data('Reddit', 'Employment', 2)
# reddit_emp_3 <- load_data('Reddit', 'Employment', 3)
# reddit_emp_4 <- load_data('Reddit', 'Employment', 4)

reddit_vac_1 <- load_data('Reddit', 'Vaccination', 1)
twitter_emp_1 <- load_data('Twitter', 'Employment', 1)
twitter_vac_1 <- load_data('Twitter', 'Vaccination', 1)
```

```{r}
# # Cleaning: stage 1b
# 
# ## Employment
# reddit_emp_1_c1b <- clean_stage1b(reddit_emp_1, 'Reddit')
# reddit_emp_2_c1b <- clean_stage1b(reddit_emp_2, 'Reddit')
# reddit_emp_3_c1b <- clean_stage1b(reddit_emp_3, 'Reddit')
# reddit_emp_4_c1b <- clean_stage1b(reddit_emp_4, 'Reddit')
# 
# save_c(reddit_emp_1_c1b, 'Reddit', 'Employment', 1, '1b')
# save_c(reddit_emp_2_c1b, 'Reddit', 'Employment', 2, '1b')
# save_c(reddit_emp_3_c1b, 'Reddit', 'Employment', 3, '1b')
# save_c(reddit_emp_4_c1b, 'Reddit', 'Employment', 4, '1b')

twitter_emp_1_c1b <- clean_stage1b(twitter_emp_1, 'Twitter')
save_c(twitter_emp_1_c1b, 'Twitter', 'Employment', 1, '1b')

## Vaccination
reddit_vac_1_c1b <- clean_stage1b(reddit_vac_1, 'Reddit')
save_c(reddit_vac_1_c1b, 'Reddit', 'Vaccination', 1, '1b')

twitter_vac_1_c1b <- clean_stage1b(twitter_vac_1, 'Twitter')
save_c(twitter_vac_1_c1b, 'Twitter', 'Vaccination', 1, '1b')
```

```{r}
# # Cleaning: stage 2
# 
# ## Employment
# reddit_emp_1_c2 <- clean_stage2(reddit_emp_1_c1b, 'Reddit')
# reddit_emp_2_c2 <- clean_stage2(reddit_emp_2_c1b, 'Reddit')
# reddit_emp_3_c2 <- clean_stage2(reddit_emp_3_c1b, 'Reddit')
# reddit_emp_4_c2 <- clean_stage2(reddit_emp_4_c1b, 'Reddit')
# 
# save_c(reddit_emp_1_c2, 'Reddit', 'Employment', 1, '2')
# save_c(reddit_emp_2_c2, 'Reddit', 'Employment', 2, '2')
# save_c(reddit_emp_3_c2, 'Reddit', 'Employment', 3, '2')
# save_c(reddit_emp_4_c2, 'Reddit', 'Employment', 4, '2')

twitter_emp_1_c2 <- clean_stage2(twitter_emp_1_c1b, 'Twitter')
save_c(twitter_emp_1_c2, 'Twitter', 'Employment', 1, '2')

## Vaccination
reddit_vac_1_c2 <- clean_stage2(reddit_vac_1_c1b, 'Reddit')
save_c(reddit_vac_1_c2, 'Reddit', 'Vaccination', 1, '2')

twitter_vac_1_c2 <- clean_stage2(twitter_vac_1_c1b, 'Twitter')
save_c(twitter_vac_1_c2, 'Twitter', 'Vaccination', 1, '2')

```



